\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-24 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Section V

\begin{table}[t]
\centering
\begin{tabular}{| l | l |} 
\hline
Description & Values\\
\hline\hline
&\\
frequency & $f_{0} = 60$ Hz\\
&\\
inertia & $m_{i}\in{\rm{Unif}}\left([2,12]\right)/2\pi f_{0}$\\
& \\
damping coefficient & $\gamma_{i}\in{\rm{Unif}}\left([20,30]\right)/2\pi f_{0}$\\
& \\
diffusion coefficient & $\sigma_{i}\in{\rm{Unif}}\left([1,5]\right)$\\
& \\
tangent of phase shift & $\tan\varphi_{ij}\in{\rm{Unif}}\left([0,0.25]\right)$\\
& \\
effective power input & $P_{i}\in{\rm{Unif}}\left([0,10]\right)$\\
& \\
coupling coefficient & $k_{ij}\in{\rm{Unif}}\left([0.7,1.2]\right)$\\
& \\
\hline
\end{tabular}
\caption{Parameters used for the numerical simulation reported in Sec. \ref{subsec:NumSimSynthetic}. The indices $i,j\in\{1,\hdots,n\}$.}
\label{table:ParamUncertaintiesSynthetic}
\end{table}

\subsection{Synthetic Test System}\label{subsec:NumSimSynthetic}
We consider a power network with $n=20$ generators, and propagate the transient joint state PDFs supported over $\mathbb{T}^{20}\times\mathbb{R}^{20}$. We take the initial joint state PDF at $t=0$ as
\begin{align*}
\rho_{0}\equiv\rho(t=0,\theta(0),\omega(0)) = &\;{\rm{Unif}}\left([0,2\pi)^{n}\;\text{rad}\right)\\
	&\qquad\times {\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right),
\end{align*}
and the stochastic parameters as in Table \ref{table:ParamUncertaintiesSynthetic}.

>>>>

\begin{table}[t]
\centering
\begin{tabular}{| l | l |} 
\hline
Parameter description & Values\\
\hline\hline
&\\
frequency & $f_{0} = 60$ Hz\\
&\\
inertia & $m_{i}\in{\rm{Unif}}\left([2,12]\right)/2\pi f_{0}$\\
& \\
damping coefficient & $\gamma_{i}\in{\rm{Unif}}\left([20,30]\right)/2\pi f_{0}$\\
& \\
diffusion coefficient & $\sigma_{i}\in{\rm{Unif}}\left([1,5]\right)$\\
& \\
tangent of phase shift & $\tan\varphi_{ij}\in{\rm{Unif}}\left([0,0.25]\right)$\\
& \\
effective power input & $P_{i}\in{\rm{Unif}}\left([0,10]\right)$\\
& \\
coupling coefficient & $k_{ij}\begin{cases}
=0 & \text{for}\; i=j,\\
\in{\rm{Unif}}\left([0.7,1.2]\right) & \text{for}\; i\neq j.	
\end{cases}$\\
& \\
\hline
\end{tabular}
\caption{Parameters used for the numerical simulation reported in Sec. \ref{subsec:NumSimSynthetic}. The indices $i,j\in\{1,\hdots,n\}$.}
\label{table:ParamUncertaintiesSynthetic}
\end{table}

\subsection{Synthetic Test System}\label{subsec:NumSimSynthetic}
We consider a power network with $n=20$ generators, and propagate the transient joint state PDFs supported over $\mathbb{T}^{20}\times\mathbb{R}^{20}$. We take the initial joint state PDF at $t=0$ as
\begin{align*}
\rho_{0}\equiv\rho(t=0,\theta(0),\omega(0)) = &\;{\rm{Unif}}\left(\left([0,2\pi)\;\text{rad}\right)^{n}\right)\\
	&\qquad\times {\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right),
\end{align*}
and following \cite[Sec. 5]{dorfler2012synchronization}, randomly generate the parameters as in Table \ref{table:ParamUncertaintiesSynthetic}. These parameter

For $N=1000$ random samples
